Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-18 tex/sections/consensus.tex
Clarify the emergency agreement protocol and fix a typo
We had forgotten to stress that users who final-voted a value should also r-vote it.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The agreement protocol consists of two phases: the \emph{voting phase}, which selects a single proposal
and the \emph{confirmation phase} which confirms the selected proposal. The voting phase is done in rounds.
Each round lasts for approximately $\lambda$ units of time, and after $k$ rounds, the current agreement session ends
and a
new session starts. All votes and messages are tagged in a way that the messages of one session can
not be used in another session.

Users cast three type of votes: \emph{$i$-votes}, which are votes that are valid only in
round $i$, \emph{final-votes}, which are votes that are valid in any round, and \emph{c-votes}, which are votes
used only in the confirmation phase.

A user executes the following procedure
in round $r$ of the voting phase:

\paragraph{Voting Phase:}
\begin{itemize}
    \item if the user has not yet final-voted any value, he $r$-votes a single desired proposal.
    \item if he sees more than 2/3 $r$-votes for a proposal $p$, he final-votes $p$.
    \item if he sees more than 2/3 final-votes for a proposal, he goes to the confirmation phase for $p$.
    \item if $clock > r \cdot \lambda$ and $r < k$ user goes to the round $r + 1$ and if $r = k$ user starts a
    new agreement session.
\end{itemize}

\paragraph{Confirmation Phase for Proposal $p$:}
\begin{itemize}
    \item user c-votes $p$.
    \item if he sees more than 2/3 c-votes for $p$ he selects $p$ and ends the agreement protocol.
    \item if $clock > k \cdot \lambda$ user starts a new agreement session.
\end{itemize}

@@

When the emergency agreement protocol is used for electing a new reserve committee to fork the blockchain, the
confirmation phase could be skipped. In that case, the confirmation of the fork block by the appropriate committee
of validators acts like the confirmation phase.

>>>>

The emergency agreement protocol is essentially an election procedure and involves human interaction. Users need to
determine who they want to vote for by interacting with the software. As long as users can not agree upon electing a
candidate, the voting process has to continue.

The agreement protocol consists of two phases: the \emph{voting phase}, which selects a single proposal
and the \emph{confirmation phase} which confirms the selected proposal. The voting phase is done in rounds.
Each round lasts for approximately $\lambda$ units of time, and after $k$ rounds, the current \emph{agreement session}
ends and a new session starts. All votes and messages are tagged in a way that the messages of one session can
not be used in another session.

Users cast three types of vote: \emph{$r$-votes}, which are votes that are valid only in
round $r$, \emph{final-votes}, which are votes that are valid in any round, and \emph{c-votes}, which are votes
used only in the confirmation phase. Votes are weighted based on users' stakes and \texttt{online/offline} status of
users is not considered. When we say 2/3 votes, we mean the sum of the stake of voters is 2/3 of the total stake.

\newpage
A user executes the following procedure in each agreement session:
\paragraph{Voting Phase in Round $r$:}
\begin{itemize}
    \item if the user has final-voted any value, he $r$-votes his final-vote, otherwise he $r$-votes a single desired
    proposal.
    \item if he sees more than 2/3 $r$-votes for a proposal $p$, he final-votes $p$.
    \item if he sees more than 2/3 final-votes for a proposal, he goes to the confirmation phase for $p$.
    \item if $clock > r \cdot \lambda$ and $r < k$ user goes to the round $r + 1$ and if $r = k$ user starts a
    new agreement session.
\end{itemize}

\paragraph{Confirmation Phase for Proposal $p$:}
\begin{itemize}
    \item user c-votes $p$.
    \item if $clock > k \cdot \lambda$ user starts a new agreement session.
\end{itemize}

\paragraph{Termination:}
\begin{itemize}
    \item as soon as the user sees more than 2/3 c-votes for $p$ he selects $p$ and ends the agreement protocol.
\end{itemize}

@@

A honest user during a session only final-votes a single proposal. This ensures that as long as $2/3$ of the total
stake of the system is controlled by honest users, two different proposal can not get $2/3$ final-votes. However, when
a user sees $2/3$ final-votes for a proposal, he can not be sure that other users have also seen those votes and have
ended the voting phase. If enough stake is still in the voting phase the agreement protocol may confirm a
different proposal.

The final confirmation phase ensures that when a proposal gets more than $2/3$ c-votes, more than $1/3$ of
\textbf{honest} stake has ended the voting phase and hence no other proposal can be confirmed by the agreement protocol.

In unlikely circumstances, an adversary can prevent honest users from reaching agreement in a session. As an example
assume that $s$ is the total stake of users and a malicious user controls $m$ stake. We have two proposals $p_1$ and
$p_2$. In the first round all users vote for $p_1$, but only $s/3 - m$ stake sees more than $2/3$ $1$-votes. At the
next round all the remaining stake votes for $p_2$. Again, only $s/3 - m$ stake sees more than $2/3$
$2$-votes. In round $3$, the malicious user stops voting. Since $s/3 - m$ stake final-voted for $p_1$ and another
$s/3 - m$ stake final-voted for $p_2$, the remaining $s/3$ honest stake is not enough for reaching an agreement.
Therefore, after $k$ rounds the session will end without an agreement and a new session will be started.

In later agreement sessions, if honest users do not change their choices drastically or if messages are transmitted
more reliably between users, an agreement can be reached eventually.

When the emergency agreement protocol is used for electing a new reserve committee to fork the blockchain, the
confirmation phase could be skipped. In that case, the confirmation of the fork block by the appropriate committee
of validators could act like the confirmation phase.
